Figures for Paper

### 2020-11-17 paper_figures.Rmd
first update on using Rprojects and github

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,warning=FALSE)
if (!require("pacman")) install.packages("pacman")
library(pacman)
p_load("data.table",
       "tidyverse",
       "ggplot2",
       "rcompanion",
       "lme4",
       "ggpubr",
       "forcats",
       "scales",
       "here")
```

@@

new_regress %>% 
    ggplot() + 
    stat_ecdf(aes(color = call, x = log10_stmn_2_cryptic_psi_leaf_plusone))
```

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,warning=FALSE)
if (!require("pacman")) install.packages("pacman")
library(pacman)
p_load("data.table",
       "tidyverse",
       "ggplot2",
       "rcompanion",
       "lme4",
       "ggpubr",
       "forcats",
       "scales",
       "here",
       "ggthemes")
```

@@

new_regress %>% 
    ggplot() + 
    stat_ecdf(aes(color = call, x = log10_stmn_2_cryptic_psi_leaf))
```
